Autocorrelation Testing

### 2023-04-19 Fish Data Analysis/Autocorrelation Testing.qmd
Updated figures

for(i in seq(1:10)){
  print(i)

  new_autocorrs <- school_data %>% group_by(Date_Trial) %>%
                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29","2021_7_7_16","2021_3_25_7","2021_10_6_34")) %>%
                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
                              lag = i)

@@

nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("NND")+
  theme_classic()

polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("Polar")+
  theme_classic()

speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("Speed")+
  theme_classic()

groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("Groups")+
  theme_classic()

area_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), area_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("Area")+
  theme_classic()

height_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), height_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ggtitle("Area")+
  theme_classic()

lag_plots <- ggarrange(
          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot, area_lag_plot, height_lag_plot,
          ncol = 3, nrow = 2)

ggsave("Autocorrelation Figures/Different_Lag_Figures.png", lag_plots, width = 22, height = 15)

>>>>

for(i in seq(1:5)){
  print(i)

  new_autocorrs <- school_data %>% group_by(Date_Trial) %>%
                    filter(!Date_Trial %in% c("2021_3_25_30","2020_7_28_29")) %>%
                    summarise(nnd_corr = abs(cor.test(NND, lag(NND, n = i))$estimate),
                              nnd_p = cor.test(NND, lag(NND, n = i))$p.value,
                              polar_corr = abs(cor.test(School_Polar, lag(School_Polar, n = i))$estimate),
                              polar_p = cor.test(School_Polar, lag(School_Polar, n = i))$p.value,
                              speed_corr = abs(cor.test(School_Speed, lag(School_Speed, n = i))$estimate),
                              speed_p = cor.test(School_Speed, lag(School_Speed, n = i))$p.value,
                              groups_corr = abs(cor.test(Groups, lag(Groups, n = i))$estimate),
                              groups_p = cor.test(Groups, lag(Groups, n = i))$p.value,
                              area_corr = abs(cor.test(Area, lag(Area, n = i))$estimate),
                              area_p = cor.test(Area, lag(Area, n = i))$p.value,
                              height_corr = abs(cor.test(School_Height, lag(School_Height, n = i))$estimate),
                              height_p = cor.test(School_Height, lag(School_Height, n = i))$p.value,
                              lag = i)

@@

nnd_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), nnd_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("NND Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

polar_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), polar_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Polarity Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

speed_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), speed_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Speed Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

groups_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), groups_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Groups Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

area_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), area_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("Area Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

height_lag_plot <- ggplot(school_autocorrs, aes(as.factor(lag), height_corr, color = as.factor(lag)))+
  stat_summary(fun.data = mean_se, geom = "errorbar", color = "black", width = 0.25) +
  stat_summary(fun.y=mean, geom="point", size = 3) +
  ylim(0,1)+
  ylab("School Height Autocorrelation")+
  xlab("Lag Values")+
  theme_classic()+ 
  theme(legend.position = "none")

lag_plots <- ggarrange(
          nnd_lag_plot, polar_lag_plot, speed_lag_plot, groups_lag_plot,
          ncol = 2, nrow = 2,
          labels = c("A", "B", "C", "D"))

ggsave("Paper Figures/Different_Lag_Figures.png", lag_plots, width = 7, height = 7)
